---
title: "Asymptotic confidence intervals for the robust effect size index"
author: Xinyu Zhang
format: 
  pdf:
    latex_engine: pdflatex
    fontsize: 11pt
bibliography: MyLibrary.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/media/disk2/asymptotic_resi")

library(locfit)
library(rootSolve)
library(parallel) 
library(dplyr)
library(tidyr)
library(ggplot2)
library(pbmcapply)
library(matrixcalc)
library(RESI)
library(ggpubr)
library(effectsize)
library(RColorBrewer)
library(stringr)

source("functions.R")
source("test/resiPEse_Th1.R") # total derivative, theta = (phi, alpha, beta)
source("test/resiPEse_Th2.R") # partial derivative, theta = (phi, alpha, beta)
```

# Configuration

```{r}
simConfig <- list(
  # scenario setting
  nsub_linear = c(50, 100, 150, 200, 300, 400),
  nsub_logistic = c(50, 75, 100, 200, 500, 750, 1000, 1500),
  model_type = c("linear", "logistic"),
  
  # linear model
  pi_linear = 0.4,
  cohen_ratio = (1/0.4 + 1/0.6)^(-1/2),
  pi_logistic = 0.5,
  ngroup = 2,
  sigma = sqrt(2),
  error = c("normal", "gamma", "hetero"),
  
  # logistic model
  design = c("balanced", "semi-balanced", "unbalanced"),

  # simulation setting
  nsim = 1000,
  mc.cores = 40
)

# path = "/media/disk2/asymptotic_resi/simulation/simresult1" # sum of the lower triangluar
# path = "/media/disk2/asymptotic_resi/simulation/simresult2" # sum of the whole matrix for se, partial derivative
# path = "/media/disk2/asymptotic_resi/simulation/simresult3" # total derivative with phi in theta 
# path = "/media/disk2/asymptotic_resi/simulation/simresult4" # partial derivative with phi in theta
# path = "/media/disk2/asymptotic_resi/simulation/simresult5" # successful simulations
path = "/media/disk2/asymptotic_resi/simulation/simresult_paper" # final version for paper

results_linear <- expand.grid(
  model_type = "linear",
  error = simConfig$error,
  S = seq(0, 1, length.out = 5),
  nsub = simConfig$nsub_linear,
  stringsAsFactors = FALSE
) %>%
  mutate(resultfile = file.path(path, model_type, error, paste0("S", S, "/nsub", nsub)))

results_logistic <- expand.grid(
  model_type = "logistic",
  error = as.character(simConfig$design),
  S = seq(0, 0.4, length.out = 5),
  nsub = simConfig$nsub_logistic,
  stringsAsFactors = FALSE
) %>%
  mutate(resultfile = file.path(path, model_type, error,
                                paste0("S", S, "/nsub", nsub)))

results_all <- bind_rows(results_linear, results_logistic) %>% 
  arrange(model_type, error, S, nsub)

simtime_table <- bind_rows(results_linear, results_logistic) %>%
  mutate(time = NA) %>%
  dplyr::select(-resultfile)

# results_all
# simtime_table
```

# Simulation 

For linear model, normal error $\epsilon \sim N(0,\sigma^2)$, gamma error $\epsilon \sim Gamma(\alpha, \frac{\sqrt{\alpha}}{\sigma})-\sqrt{\alpha}\sigma$. For heteroskedasticity error: $\epsilon \mid X=0 \sim N(0,\sigma_0^2), \quad \epsilon \mid X = 1 \sim N(0, \sigma_1^2)$, given that $p = P(X=1)$ and $r = \frac{\sigma_1^2}{\sigma_0^2}$, $Var(\epsilon) = (1-p)\sigma_0^2 + p\sigma_1^2 =\sigma^2$. We have $\sigma_0^2 = \frac{\sigma^2}{(1-p) + pr}$, $\sigma_1^2 = 2\sigma_0^2$. $Var(\hat\beta) = \frac{\sigma_1^2}{p} + \frac{\sigma_0^2}{1-p}$, so we can compute true $\beta$.


```{r, eval=TRUE}
# sce_results <- results_all
sce_results <- results_all %>% filter(model_type == "logistic")
# sce_results <- results_all %>% filter(model_type == "linear")
simtime <- simtime_table %>% filter(model_type == "logistic")

for(sce in 1:nrow(sce_results)){
  
  set.seed(1000 + sce)
  
  # ========== Setting ========== 
  
  model_type = sce_results$model_type[sce]
  error = sce_results$error[sce]
  S = sce_results$S[sce]
  nsub = sce_results$nsub[sce]
  resultfile = sce_results$resultfile[sce]
  nsim = simConfig$nsim
  # nsim = 500

  # Track progress 
  print(resultfile) 
  dir.create(resultfile, showWarnings = FALSE, recursive = TRUE)
  
  # ========== Simulation ==========
  
  if (file.exists(file.path(resultfile, "result_dat.rds"))) {
    result_dat = readRDS(file.path(resultfile, "result_dat.rds"))
  }else{
    
  start = Sys.time()
  
  allsimresults = pbmclapply(1:nsim, function(sim){
    
    ## ========== Linear model ==========
    
    if(model_type == "linear"){
      
      p = simConfig$pi_linear
      sigma = simConfig$sigma
      dx = as.numeric(rbinom(nsub, 1, prob = p))
        
       # Generate error term
      if(error == "normal"){ # homoskedasticity
        beta_true = S * sigma / sqrt(p * (1 - p))
        error_term = rnorm(nsub, mean = 0, sd = sigma)
        
      }else if(error == "gamma"){  # homoskedasticity
        beta_true = S * sigma / sqrt(p * (1 - p))
        shape = 1.2
        error_term = rgamma(nsub, shape, rate = sqrt(shape)/sigma) - 
          sqrt(shape) * sigma
        
      }else if(error == "hetero"){ # heteroskedasticity
        r = 3
        sigma0_sq = sigma^2 / ((1 - p) + p * r)
        sigma1_sq = r * sigma0_sq
        beta_true = S * sqrt((sigma0_sq/(1-p) + sigma1_sq/p))
        error_term = rnorm(nsub, mean = 0, 
                           sd = ifelse(dx == 0, sqrt(sigma0_sq), sqrt(sigma1_sq)))
      }else{
        stop("Unsupported error type")
      }
    
      Y = 1 + beta_true * dx + error_term
      model = lm(Y ~ dx)
      
    ## ========== Logistic model ==========
      
    }else if(model_type == "logistic"){
      
      p = simConfig$pi_logistic
      dx = as.numeric(rbinom(nsub, 1, prob = p))
      
      # select the first root as true beta
      a = case_when(
        error == "balanced" ~ 0,
        error == "semi-balanced" ~ -1,
        error == "unbalanced" ~ -2)
      
      if(S == 0){
        beta_true = 0
      }else{
        beta_true = uniroot.all(function(beta) 
          S_squared(beta, alpha = a, px = p) - S^2, lower = 0, upper = 10)[1]
      }
      
      # logit link
      lin_pred = rowSums(model.matrix(~ dx)[, -1, drop = FALSE] * beta_true + a) 
      Y = rbinom(nsub, 1, prob = expit(lin_pred))
      model = glm(Y ~ dx, family = binomial)
    }
    
    # Models
    if(model_type == "linear"){
      # Cohen's d and Conhen's f
      d_res <- cohens_d(Y ~ dx, data = data.frame(Y = Y, dx = dx))
      f_res <- cohens_f(anova(model), alternative = "two.sided")
      # RESI
      ## Signed
      th1_const_signed <- resiPEse_Th1(model, variable = "dx", type = "const", unsigned = FALSE)
      th1_hc_signed <- resiPEse_Th1(model, variable = "dx", type = "HC3", unsigned = FALSE)
      th2_const_signed <- resiPEse_Th2(model, variable = "dx", type = "const", unsigned = FALSE)
      th2_hc_signed <- resiPEse_Th2(model, variable = "dx", type = "HC3", unsigned = FALSE)
      
      ## Unsigned
      th1_const_unsigned <- resiPEse_Th1(model, variable = "dx", type = "const", unsigned = TRUE)
      th1_hc_unsigned <- resiPEse_Th1(model, variable = "dx", type = "HC3", unsigned = TRUE)
      th2_const_unsigned <- resiPEse_Th2(model, variable = "dx", type = "const", unsigned = TRUE)
      th2_hc_unsigned <- resiPEse_Th2(model, variable = "dx", type = "HC3", unsigned = TRUE)
      
      
    }else{
      # No Cohen's d and Conhen's f
      d_res = data.frame(Cohens_d = NA, CI_low = NA, CI_high = NA)
      f_res = data.frame(Cohens_f = NA, CI_low = NA, CI_high = NA)
      # RESI
      ## Signed
      th1_const_signed <- resiPEse_Th1(model, variable = "dx", 
                                       type = "const", unsigned = FALSE)
      th1_hc_signed <- resiPEse_Th1(model, variable = "dx", 
                                    type = "HC0", unsigned = FALSE)
      th2_const_signed <- resiPEse_Th2(model, variable = "dx", 
                                       type = "const", unsigned = FALSE)
      th2_hc_signed <- resiPEse_Th2(model, variable = "dx", 
                                    type = "HC0", unsigned = FALSE)
      
      ## Unsigned
      th1_const_unsigned <- resiPEse_Th1(model, variable = "dx", 
                                         type = "const", unsigned = TRUE)
      th1_hc_unsigned <- resiPEse_Th1(model, variable = "dx", 
                                      type = "HC0", unsigned = TRUE)
      th2_const_unsigned <- resiPEse_Th2(model, variable = "dx", 
                                         type = "const", unsigned = TRUE)
      th2_hc_unsigned <- resiPEse_Th2(model, variable = "dx", 
                                      type = "HC0", unsigned = TRUE)
      
    }
    
    data.frame(
      # Effect size
      ## Signed
      RESI1_const_signed = th1_const_signed$RESI_Xinyu, 
      RESI1_hc_signed = th1_hc_signed$RESI_Xinyu, 
      RESI2_const_signed = th2_const_signed$RESI_Xinyu, 
      RESI2_hc_signed = th2_hc_signed$RESI_Xinyu, 
      
      ## Unsigned
      RESI1_const_unsigned = th1_const_unsigned$RESI_Xinyu, 
      RESI1_hc_unsigned = th1_hc_unsigned$RESI_Xinyu, 
      RESI2_const_unsigned = th2_const_unsigned$RESI_Xinyu, 
      RESI2_hc_unsigned = th2_hc_unsigned$RESI_Xinyu, 
      
      ## Other
      Cohens_d = -d_res$Cohens_d, 
      Cohens_f = f_res$Cohens_f, 
      
      # SE
      ## Signed
      SE1_const_signed = th1_const_signed$RESI.SE, 
      SE1_hc_signed = th1_hc_signed$RESI.SE, 
      SE2_const_signed = th2_const_signed$RESI.SE, 
      SE2_hc_signed = th2_hc_signed$RESI.SE, 
      
      ## Unsigned
      SE1_const_unsigned = th1_const_unsigned$RESI.SE, 
      SE1_hc_unsigned = th1_hc_unsigned$RESI.SE, 
      SE2_const_unsigned = th2_const_unsigned$RESI.SE, 
      SE2_hc_unsigned = th2_hc_unsigned$RESI.SE, 
      
      # Coverage
      ## Signed
      LCI1_const_signed = th1_const_signed$LCI, 
      UCI1_const_signed = th1_const_signed$UCI, 
      LCI1_hc_signed = th1_hc_signed$LCI, 
      UCI1_hc_signed = th1_hc_signed$UCI, 
      LCI2_const_signed = th2_const_signed$LCI, 
      UCI2_const_signed = th2_const_signed$UCI, 
      LCI2_hc_signed = th2_hc_signed$LCI, 
      UCI2_hc_signed = th2_hc_signed$UCI, 
      
      ## Unsigned
      LCI1_const_unsigned = th1_const_unsigned$LCI, 
      UCI1_const_unsigned = th1_const_unsigned$UCI, 
      LCI1_hc_unsigned = th1_hc_unsigned$LCI, 
      UCI1_hc_unsigned = th1_hc_unsigned$UCI, 
      LCI2_const_unsigned = th2_const_unsigned$LCI, 
      UCI2_const_unsigned = th2_const_unsigned$UCI, 
      LCI2_hc_unsigned = th2_hc_unsigned$LCI, 
      UCI2_hc_unsigned = th2_hc_unsigned$UCI, 
      
      ## Other
      LCI_Cohens_d = -d_res$CI_high, 
      UCI_Cohens_d = -d_res$CI_low,
      LCI_Cohens_f = f_res$CI_low, 
      UCI_Cohens_f = f_res$CI_high)
    
  }, mc.cores = simConfig$mc.cores,  mc.set.seed = TRUE)
  
  simtime$time[sce] = Sys.time() - start
  
  # ========== Organization ==========
  
  result_dat = do.call(rbind, allsimresults)
  saveRDS(result_dat, file = file.path(resultfile, "result_dat.rds"))
  }
  
  # Effect Size
  ## Signed
  sce_results[sce, "Mean_RESI1_const_signed"] = mean(result_dat$RESI1_const_signed, na.rm = T)
  sce_results[sce, "Mean_RESI1_hc_signed"] = mean(result_dat$RESI1_hc_signed, na.rm = T)
  sce_results[sce, "Mean_RESI2_const_signed"] = mean(result_dat$RESI2_const_signed, na.rm = T)
  sce_results[sce, "Mean_RESI2_hc_signed"] = mean(result_dat$RESI2_hc_signed, na.rm = T)
  
  ## Unsigned
  sce_results[sce, "Mean_RESI1_const_unsigned"] = mean(result_dat$RESI1_const_unsigned, na.rm = T)
  sce_results[sce, "Mean_RESI1_hc_unsigned"] = mean(result_dat$RESI1_hc_unsigned, na.rm = T)
  sce_results[sce, "Mean_RESI2_const_unsigned"] = mean(result_dat$RESI2_const_unsigned, na.rm = T)
  sce_results[sce, "Mean_RESI2_hc_unsigned"] = mean(result_dat$RESI2_hc_unsigned, na.rm = T)
  
  # sce_results[sce, "Mean_RESI_Megan_const"] = mean(result_dat$RESI_Megan_const, na.rm = T)
  # sce_results[sce, "Mean_RESI_Megan_hc"] = mean(result_dat$RESI_Megan_hc, na.rm = T)
  sce_results[sce, "Mean_Cohens_d"] = mean(result_dat$Cohens_d, na.rm = T)
  sce_results[sce, "Mean_Cohens_f"] = mean(result_dat$Cohens_f, na.rm = T)
  
  
  # Variance
  ## Signed
  sce_results[sce, "Emp_Var1_const_signed"] = var(result_dat$RESI1_const_signed, na.rm = TRUE)
  sce_results[sce, "Emp_Var1_hc_signed"]    = var(result_dat$RESI1_hc_signed, na.rm = TRUE)
  sce_results[sce, "Emp_Var2_const_signed"] = var(result_dat$RESI2_const_signed, na.rm = TRUE)
  sce_results[sce, "Emp_Var2_hc_signed"]    = var(result_dat$RESI2_hc_signed, na.rm = TRUE)

  ## Unsigned
  sce_results[sce, "Emp_Var1_const_unsigned"] = var(result_dat$RESI1_const_unsigned, na.rm = TRUE)
  sce_results[sce, "Emp_Var1_hc_unsigned"]    = var(result_dat$RESI1_hc_unsigned, na.rm = TRUE)
  sce_results[sce, "Emp_Var2_const_unsigned"] = var(result_dat$RESI2_const_unsigned, na.rm = TRUE)
  sce_results[sce, "Emp_Var2_hc_unsigned"]    = var(result_dat$RESI2_hc_unsigned, na.rm = TRUE)

  ## Signed
  sce_results[sce, "MeanAnalytic_Var1_const_signed"] = mean(result_dat$SE1_const_signed^2, na.rm = TRUE)
  sce_results[sce, "MeanAnalytic_Var1_hc_signed"]    = mean(result_dat$SE1_hc_signed^2, na.rm = TRUE)
  sce_results[sce, "MeanAnalytic_Var2_const_signed"] = mean(result_dat$SE2_const_signed^2, na.rm = TRUE)
  sce_results[sce, "MeanAnalytic_Var2_hc_signed"]    = mean(result_dat$SE2_hc_signed^2, na.rm = TRUE)

  ## Unsigned
  sce_results[sce, "MeanAnalytic_Var1_const_unsigned"] = mean(result_dat$SE1_const_unsigned^2, na.rm = TRUE)
  sce_results[sce, "MeanAnalytic_Var1_hc_unsigned"]    = mean(result_dat$SE1_hc_unsigned^2, na.rm = TRUE)
  sce_results[sce, "MeanAnalytic_Var2_const_unsigned"] = mean(result_dat$SE2_const_unsigned^2, na.rm = TRUE)
  sce_results[sce, "MeanAnalytic_Var2_hc_unsigned"]    = mean(result_dat$SE2_hc_unsigned^2, na.rm = TRUE)



  # Coverage
  ## Signed
  sce_results[sce, "Lcoverage1_const_signed"] = mean(result_dat$LCI1_const_signed <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage1_const_signed"] = mean(result_dat$UCI1_const_signed >= S, na.rm = TRUE)
  sce_results[sce, "Coverage1_const_signed"]  = mean(result_dat$LCI1_const_signed <= S & 
                                                       result_dat$UCI1_const_signed >= S, na.rm = TRUE)
  
  sce_results[sce, "Lcoverage1_hc_signed"] = mean(result_dat$LCI1_hc_signed <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage1_hc_signed"] = mean(result_dat$UCI1_hc_signed >= S, na.rm = TRUE)
  sce_results[sce, "Coverage1_hc_signed"]  = mean(result_dat$LCI1_hc_signed <= S & 
                                                    result_dat$UCI1_hc_signed >= S, na.rm = TRUE)
  
  sce_results[sce, "Lcoverage2_const_signed"] = mean(result_dat$LCI2_const_signed <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage2_const_signed"] = mean(result_dat$UCI2_const_signed >= S, na.rm = TRUE)
  sce_results[sce, "Coverage2_const_signed"]  = mean(result_dat$LCI2_const_signed <= S & 
                                                       result_dat$UCI2_const_signed >= S, na.rm = TRUE)
  
  sce_results[sce, "Lcoverage2_hc_signed"] = mean(result_dat$LCI2_hc_signed <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage2_hc_signed"] = mean(result_dat$UCI2_hc_signed >= S, na.rm = TRUE)
  sce_results[sce, "Coverage2_hc_signed"]  = mean(result_dat$LCI2_hc_signed <= S & 
                                                    result_dat$UCI2_hc_signed >= S, na.rm = TRUE)
  
  # Unsigned
  sce_results[sce, "Lcoverage1_const_unsigned"] = mean(result_dat$LCI1_const_unsigned <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage1_const_unsigned"] = mean(result_dat$UCI1_const_unsigned >= S, na.rm = TRUE)
  sce_results[sce, "Coverage1_const_unsigned"]  = mean(result_dat$LCI1_const_unsigned <= S & 
                                                         result_dat$UCI1_const_unsigned >= S, na.rm = TRUE)
  
  sce_results[sce, "Lcoverage1_hc_unsigned"] = mean(result_dat$LCI1_hc_unsigned <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage1_hc_unsigned"] = mean(result_dat$UCI1_hc_unsigned >= S, na.rm = TRUE)
  sce_results[sce, "Coverage1_hc_unsigned"]  = mean(result_dat$LCI1_hc_unsigned <= S & 
                                                      result_dat$UCI1_hc_unsigned >= S, na.rm = TRUE)
  
  sce_results[sce, "Lcoverage2_const_unsigned"] = mean(result_dat$LCI2_const_unsigned <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage2_const_unsigned"] = mean(result_dat$UCI2_const_unsigned >= S, na.rm = TRUE)
  sce_results[sce, "Coverage2_const_unsigned"]  = mean(result_dat$LCI2_const_unsigned <= S & 
                                                         result_dat$UCI2_const_unsigned >= S, na.rm = TRUE)
  
  sce_results[sce, "Lcoverage2_hc_unsigned"] = mean(result_dat$LCI2_hc_unsigned <= S, na.rm = TRUE)
  sce_results[sce, "Ucoverage2_hc_unsigned"] = mean(result_dat$UCI2_hc_unsigned >= S, na.rm = TRUE)
  sce_results[sce, "Coverage2_hc_unsigned"]  = mean(result_dat$LCI2_hc_unsigned <= S & 
                                                      result_dat$UCI2_hc_unsigned >= S, na.rm = TRUE)
  
  ## Other
  sce_results[sce, "Cohens_d_Coverage"] = mean(result_dat$LCI_Cohens_d <= S * 1/simConfig$cohen_ratio &
                                                 result_dat$UCI_Cohens_d >= S * 1/simConfig$cohen_ratio, 
                                               na.rm = T)
  sce_results[sce, "Cohens_f_Coverage"] = mean(result_dat$LCI_Cohens_f <= S &
                                                 result_dat$UCI_Cohens_f >= S, na.rm = T)
}

# saveRDS(simtime, file.path(path, "linear/simtime.rds"))
# saveRDS(sce_results, file.path(path, "linear/sce_results_quasi_04.rds"))
# save.image(file = file.path(path, "linear/Allsces_quasi_04.RData"))

saveRDS(simtime, file.path(path, "logistic/simtime.rds"))
saveRDS(sce_results, file.path(path, "logistic/sce_results_05.rds"))
save.image(file = file.path(path, "logistic/Allsces_05.RData"))

# save.image(file = file.path(path, "Allsces.RData"))
# saveRDS(sce_results, file.path(path, "sce_results.rds"))

stop()
```

# Plot

## Linear model

```{r}
sce_results <- readRDS("/media/disk2/asymptotic_resi/simulation/simresult_paper/linear/sce_results_quasi_04.rds")

linear_results <- sce_results %>% filter(model_type == "linear") %>%
  mutate(S_label = factor(S, labels = paste0("S = ", unique(S))),
         error = factor(error, levels = c("normal", "gamma", "hetero"), 
                        labels = c("Normal", "Gamma", "Hetero")))

# Bias comparison
linear_bias <- linear_results %>%
  mutate(Cohen_f_Bias = Mean_Cohens_f - S,
         Cohen_d_Bias = Mean_Cohens_d * simConfig$cohen_ratio - S,
         # Package_Bias_const = Mean_RESI_Megan_const - S,
         # Package_Bias_hc = Mean_RESI_Megan_hc - S,
         RESI1_Bias_const_signed = Mean_RESI1_const_signed - S,
         RESI1_Bias_hc_signed = Mean_RESI1_hc_signed - S,
         RESI1_Bias_const_unsigned = Mean_RESI1_const_unsigned - S,
         RESI1_Bias_hc_unsigned = Mean_RESI1_hc_unsigned - S,
         
         RESI2_Bias_const_signed = Mean_RESI2_const_signed - S,
         RESI2_Bias_hc_signed = Mean_RESI2_hc_signed - S,
         RESI2_Bias_const_unsigned = Mean_RESI2_const_unsigned - S,
         RESI2_Bias_hc_unsigned = Mean_RESI2_hc_unsigned - S) 

long_linear_bias <- pivot_longer(linear_bias, 
                                 cols = contains("_Bias"), 
                                 names_to = "method",
                                 values_to = "bias") %>% 
  mutate(
    label = case_when(
      str_detect(method, "const") ~ "const",
      str_detect(method, "hc") ~ "hc",
      TRUE ~ "other"  
    ),
    method_base = str_remove(method, "_(const|hc)$")) %>%
  mutate(method = factor(method, levels = c("Cohen_f_Bias", "Cohen_d_Bias", 
                                            "Package_Bias_const", "Package_Bias_hc", 
                                            "RESI1_Bias_const_signed", "RESI1_Bias_hc_signed",
                                            "RESI1_Bias_const_unsigned", "RESI1_Bias_hc_unsigned",
                                            "RESI2_Bias_const_signed", "RESI2_Bias_hc_signed",
                                            "RESI2_Bias_const_unsigned", "RESI2_Bias_hc_unsigned"))) %>%
  select(model_type, error, S, nsub, S_label, method, bias, label) %>%
  mutate(S_label = paste0("S[beta] == ", S))

bias_label <- c(
      "RESI1_Bias_const_signed" = "Signed RESI (Param)",
      "RESI1_Bias_hc_signed"    = "Signed RESI (Robust)",
      "RESI1_Bias_const_unsigned" = "Unsigned RESI (Param)",
      "RESI1_Bias_hc_unsigned"    = "Unsigned RESI (Robust)",
      
      "RESI2_Bias_const_signed" = "Signed RESI2 (Param)",
      "RESI2_Bias_hc_signed"    = "Signed RESI2 (Robust)",
      "RESI2_Bias_const_unsigned" = "Unsigned RESI2 (Param)",
      "RESI2_Bias_hc_unsigned"    = "Unsigned RESI2 (Robust)",
      
      "Cohen_d_Bias"        = "Cohen's d",
      "Cohen_f_Bias"        = "Cohen's f"
      # "Package_Bias_const"  = "Package (Param)",
      # "Package_Bias_hc"     = "Package (HC3)"
    )
coverage_label <- c(
  "Cohens_d_Coverage" = "Cohen's d",
  "Cohens_f_Coverage" = "Cohen's f",
  "Coverage1_const_signed" = "Signed RESI (Param)",
  "Coverage1_hc_signed"    = "Signed RESI (Robust)",
  "Coverage1_const_unsigned" = "Unsigned RESI (Param)",
  "Coverage1_hc_unsigned"    = "Unsigned RESI (Robust)",
  
  "Coverage2_const_signed" = "Signed RESI (Param)",
  "Coverage2_hc_signed"    = "Signed RESI (Robust)",
  "Coverage2_const_unsigned" = "Unsigned RESI (Param)",
  "Coverage2_hc_unsigned"    = "Unsigned RESI (Robust)"
)

bias_color <- c(
  "RESI1_Bias_const_signed" = "#619CFF", 
  "RESI1_Bias_hc_signed" = "#619CFF", 
  "RESI1_Bias_const_unsigned" = "#619CFF", 
  "RESI1_Bias_hc_unsigned" = "#619CFF", 
  "RESI2_Bias_const_signed" = "#E69F00", 
  "RESI2_Bias_hc_signed" = "#E69F00", 
  "RESI2_Bias_const_unsigned" = "#E69F00", 
  "RESI2_Bias_hc_unsigned" = "#E69F00", 
  "Cohen_d_Bias"  = "#F8766D", 
  "Cohen_f_Bias"  = "#F8766D"
)

coverage_color <- c(
  "Coverage1_const_signed" = "#619CFF", 
  "Coverage1_hc_signed" = "#619CFF", 
  "Coverage1_const_unsigned" = "#619CFF", 
  "Coverage1_hc_unsigned" = "#619CFF", 
  "Coverage2_const_signed" = "#E69F00", 
  "Coverage2_hc_signed" = "#E69F00",
  "Coverage2_const_unsigned" = "#E69F00", 
  "Coverage2_hc_unsigned" = "#E69F00",
  "Cohens_d_Coverage" = "#F8766D",
  "Cohens_f_Coverage" = "#F8766D"
)

bias_linetype <- c(
  "Cohen_f_Bias"       = "solid",
  "Cohen_d_Bias"       = "solid",
  # "Package_Bias_const" = "dashed",
  # "Package_Bias_hc"    = "solid",
  "RESI1_Bias_const_signed"= "solid",
  "RESI1_Bias_hc_signed"   = "dashed",
  "RESI1_Bias_const_unsigned"= "solid",
  "RESI1_Bias_hc_unsigned"   = "dashed",
  "RESI2_Bias_const_signed" = "solid", 
  "RESI2_Bias_hc_signed" = "dashed", 
  "RESI2_Bias_const_unsigned" = "solid", 
  "RESI2_Bias_hc_unsigned" = "dashed")


coverage_linetype <- c(
  "Coverage1_const_signed" = "solid", 
  "Coverage1_hc_signed" = "dashed", 
  "Coverage1_const_unsigned" = "solid", 
  "Coverage1_hc_unsigned" = "dashed", 
  "Coverage2_const_signed" = "solid", 
  "Coverage2_hc_signed" = "dashed",
  "Coverage2_const_unsigned" = "solid", 
  "Coverage2_hc_unsigned" = "dashed",
  "Cohens_d_Coverage" = "solid",
  "Cohens_f_Coverage" = "solid"
)


# Coverage comparison
long_linear_coverage <- pivot_longer(linear_results, 
                                     cols = contains("Coverage", ignore.case = TRUE), 
                                     names_to = "method",
                                     values_to = "coverage") %>%
  mutate(
    label = case_when(
      str_detect(method, "const") ~ "const",
      str_detect(method, "hc") ~ "hc",
      TRUE ~ "other"  
    ),
    method_base = str_remove(method, "_(const|hc)$")) %>%
    select(model_type, error, S, nsub, S_label, method, coverage, label) %>%
  mutate(S_label = paste0("S[beta] == ", S))

# bias (unsigned RESI + Cohen's f)
p1 <- ggplot(data = long_linear_bias %>% 
               filter(method %in% c("Cohen_f_Bias", 
                                    "RESI1_Bias_const_unsigned",
                                    "RESI1_Bias_hc_unsigned"))) + 
  geom_line(aes(x = nsub, y = bias, color = method, linetype = method)) + 
  facet_grid(
    error ~ S_label,
      labeller = labeller(S_label = label_parsed, error = label_value)
  ) + 
  theme_bw() + 
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(title = "Bias (Unsigned Effect Size)", 
       x = "Number of subjects", y = "Bias", color = "Method", 
       linetype = "Method") +
  theme(legend.position = "top") +
  scale_color_manual(values = bias_color, labels = bias_label) +
  scale_linetype_manual(values = bias_linetype, labels = bias_label)

# coverage (unsigned RESI + Cohen's f)
p2 <- ggplot(data = long_linear_coverage %>% 
               filter(method %in% c("Cohens_f_Coverage", 
                                    "Coverage1_const_unsigned", "Coverage1_hc_unsigned"))) +
  geom_line(aes(x = nsub, y = coverage, color = method, linetype = method)) + 
  facet_grid(
    error ~ S_label,
      labeller = labeller(S_label = label_parsed, error = label_value)
  ) +
  theme_bw() + 
  geom_hline(yintercept = 0.95, linetype = "dotted") +
  labs(title = "Coverage (Unsigned Effect Size)", 
       x = "Number of subjects", y = "Coverage", color = "Method", 
       linetype = "Method") + 
  theme(legend.position = "top")  +
  scale_color_manual(values = coverage_color, labels = coverage_label) +
  scale_linetype_manual(values = coverage_linetype, labels = coverage_label)

# Bias (signed RESI + cohen's d)
p3 <- ggplot(long_linear_bias %>% 
               filter(method %in% c("Cohen_d_Bias", "RESI1_Bias_const_signed",
                                    "RESI1_Bias_hc_signed"))) + 
  geom_line(aes(x = nsub, y = bias, color = method, linetype = method)) + 
  facet_grid(
    error ~ S_label,
      labeller = labeller(S_label = label_parsed, error = label_value)
  ) + 
  theme_bw() + 
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(title = "Bias (Signed Effect Size)", 
       x = "Number of subjects", y = "Bias", color = "Method", 
       linetype = "Method") +
  theme(legend.position = "top") +
  scale_color_manual(values = bias_color,  labels = bias_label) +
  scale_linetype_manual(values = bias_linetype,labels = bias_label)

# coverage (signed RESI + cohen's d)
p4 <- ggplot(data = long_linear_coverage %>% 
               filter(method %in% c("Cohens_d_Coverage", 
                                    "Coverage1_const_signed", "Coverage1_hc_signed"))) +
  geom_line(aes(x = nsub, y = coverage, color = method, linetype = method)) + 
  facet_grid(
    error ~ S_label,
      labeller = labeller(S_label = label_parsed, error = label_value)
  ) + 
  theme_bw() + 
  geom_hline(yintercept = 0.95, linetype = "dotted") +
  labs(title = "Coverage (Signed Effect Size)", 
       x = "Number of subjects", y = "Coverage", color = "Method", 
       linetype = "Method") + 
  theme(legend.position = "top")  +
  scale_color_manual(values = coverage_color, labels = coverage_label) +
  scale_linetype_manual(values = coverage_linetype,labels = coverage_label)
```


```{r, fig.width=12, fig.height=5}
ggarrange(p1, p2)
# ggsave("/media/disk2/asymptotic_resi/simulation/simresult_paper/linear/unsigned.png", height = 5, width = 12, dpi = 600)
ggarrange(p3, p4)
# ggsave("/media/disk2/asymptotic_resi/simulation/simresult_paper/linear/signed.png", height = 5, width = 12, dpi = 600)
```

## Logistic model

```{r}
sce_results <- readRDS("/media/disk2/asymptotic_resi/simulation/simresult_paper/logistic/sce_results_05.rds")
logistic_results <- sce_results %>% filter(model_type == "logistic")  %>% 
  mutate(S_label = factor(S, labels = paste0("S = ", unique(S))),
         error = factor(error, levels = c("balanced", "semi-balanced", "unbalanced"), 
                        labels = c("Balanced", "Semi-balanced", "Unbalanced")))

# Bias comparison
logistic_bias <- logistic_results %>%
  mutate(
    # Cohen_f_Bias = Mean_Cohens_f - S,
         # Cohen_d_Bias = Mean_Cohens_d * simConfig$cohen_ratio - S,
         # Package_Bias_const = Mean_RESI_Megan_const - S,
         # Package_Bias_hc = Mean_RESI_Megan_hc - S,
         RESI1_Bias_const_signed = Mean_RESI1_const_signed - S,
         RESI1_Bias_hc_signed = Mean_RESI1_hc_signed - S,
         RESI1_Bias_const_unsigned = Mean_RESI1_const_unsigned - S,
         RESI1_Bias_hc_unsigned = Mean_RESI1_hc_unsigned - S,
         
         RESI2_Bias_const_signed = Mean_RESI2_const_signed - S,
         RESI2_Bias_hc_signed = Mean_RESI2_hc_signed - S,
         RESI2_Bias_const_unsigned = Mean_RESI2_const_unsigned - S,
         RESI2_Bias_hc_unsigned = Mean_RESI2_hc_unsigned - S) 

long_logistic_bias <- pivot_longer(logistic_bias, 
                                 cols = contains("_Bias"), 
                                 names_to = "method",
                                 values_to = "bias") %>%
  mutate(
    label = case_when(
      str_detect(method, "const") ~ "const",
      str_detect(method, "hc") ~ "hc",
      TRUE ~ "other"  
    ),
    method_base = str_remove(method, "_(const|hc)$")
  ) %>%
  mutate(method = factor(method, levels = c("Cohen_f_Bias", "Cohen_d_Bias", 
                                            # "Package_Bias_const", "Package_Bias_hc", 
                                            "RESI1_Bias_const_signed", "RESI1_Bias_hc_signed",
                                            "RESI1_Bias_const_unsigned", "RESI1_Bias_hc_unsigned",
                                            "RESI2_Bias_const_signed", "RESI2_Bias_hc_signed",
                                            "RESI2_Bias_const_unsigned", "RESI2_Bias_hc_unsigned"))) %>%
  select(model_type, error, S, nsub, S_label, method, bias, label) %>%
  mutate(S_label = paste0("S[beta] == ", S))


bias_label <- c(
      "RESI1_Bias_const_signed" = "Signed RESI (Param)",
      "RESI1_Bias_hc_signed"    = "Signed RESI (Robust)",
      "RESI1_Bias_const_unsigned" = "Unsigned RESI (Param)",
      "RESI1_Bias_hc_unsigned"    = "Unsigned RESI (Robust)",
      
      "RESI2_Bias_const_signed" = "Signed RESI2 (Param)",
      "RESI2_Bias_hc_signed"    = "Signed RESI2 (Robust)",
      "RESI2_Bias_const_unsigned" = "Unsigned RESI2 (Param)",
      "RESI2_Bias_hc_unsigned"    = "Unsigned RESI2 (Robust)",
      
      "Cohen_d_Bias"        = "Cohen's d",
      "Cohen_f_Bias"        = "Cohen's f"
      # "Package_Bias_const"  = "Package (Param)",
      # "Package_Bias_hc"     = "Package (HC3)"
    )
coverage_label <- c(
  "Cohens_d_Coverage" = "Cohen's d",
  "Cohens_f_Coverage" = "Cohen's f",
  "Coverage1_const_signed" = "Signed RESI (Param)",
  "Coverage1_hc_signed"    = "Signed RESI (Robust)",
  "Coverage1_const_unsigned" = "Unsigned RESI (Param)",
  "Coverage1_hc_unsigned"    = "Unsigned RESI (Robust)",
  
  "Coverage2_const_signed" = "Signed RESI (Param)",
  "Coverage2_hc_signed"    = "Signed RESI (Robust)",
  "Coverage2_const_unsigned" = "Unsigned RESI (Param)",
  "Coverage2_hc_unsigned"    = "Unsigned RESI (Robust)"
)

bias_color <- c(
  "RESI1_Bias_const_signed" = "#33CC66", 
  "RESI1_Bias_hc_signed" = "#33CC66", 
  "RESI1_Bias_const_unsigned" = "#CC33FF", 
  "RESI1_Bias_hc_unsigned" = "#CC33FF"
)

coverage_color <- c(
  "Coverage1_const_signed" = "#33CC66", 
  "Coverage1_hc_signed" = "#33CC66", 
  "Coverage1_const_unsigned" = "#CC33FF", 
  "Coverage1_hc_unsigned" = "#CC33FF"
)

bias_linetype <- c(
  "Cohen_f_Bias"       = "solid",
  "Cohen_d_Bias"       = "solid",
  # "Package_Bias_const" = "dashed",
  # "Package_Bias_hc"    = "solid",
  "RESI1_Bias_const_signed"= "solid",
  "RESI1_Bias_hc_signed"   = "dashed",
  "RESI1_Bias_const_unsigned"= "solid",
  "RESI1_Bias_hc_unsigned"   = "dashed",
  "RESI2_Bias_const_signed" = "solid", 
  "RESI2_Bias_hc_signed" = "dashed", 
  "RESI2_Bias_const_unsigned" = "solid", 
  "RESI2_Bias_hc_unsigned" = "dashed")


coverage_linetype <- c(
  "Coverage1_const_signed" = "solid", 
  "Coverage1_hc_signed" = "dashed", 
  "Coverage1_const_unsigned" = "solid", 
  "Coverage1_hc_unsigned" = "dashed", 
  "Coverage2_const_signed" = "solid", 
  "Coverage2_hc_signed" = "dashed",
  "Coverage2_const_unsigned" = "solid", 
  "Coverage2_hc_unsigned" = "dashed",
  "Cohens_d_Coverage" = "solid",
  "Cohens_f_Coverage" = "solid"
)

# Coverage comparison
long_logistic_coverage <- pivot_longer(logistic_results, 
                                     cols = contains("Coverage", ignore.case = TRUE), 
                                     names_to = "method",
                                     values_to = "coverage") %>%
  mutate(
    label = case_when(
      str_detect(method, "const") ~ "const",
      str_detect(method, "hc") ~ "hc",
      TRUE ~ "other"  
    ),
    method_base = str_remove(method, "_(const|hc)$")
  ) %>%
    select(model_type, error, S, nsub, S_label, method, coverage, label) %>%
  mutate(S_label = paste0("S[beta] == ", S))


p1 <- ggplot(data = long_logistic_bias %>% 
               filter(method %in% c("RESI1_Bias_const_signed",
                                    "RESI1_Bias_hc_signed",
                                    "RESI1_Bias_const_unsigned",
                                    "RESI1_Bias_hc_unsigned"))) + 
  geom_line(aes(x = nsub, y = bias, color = method, linetype = method)) + 
  facet_grid(
    error ~ S_label,
      labeller = labeller(S_label = label_parsed, error = label_value)
  ) + 
  theme_bw() + 
  geom_hline(yintercept = 0, linetype = "dotted") + 
  labs(title = "RESI Bias", 
       x = "Number of subjects", y = "Bias", color = "Method", 
       linetype = "Method") + 
  theme(legend.position = "top") + 
  scale_x_continuous(breaks = c(100, 500, 1000, 1500), 
                     guide = guide_axis(angle = 45)) + 
  scale_color_manual(values = bias_color, labels = bias_label) +
  scale_linetype_manual(values = bias_linetype, labels = bias_label)

p2 <- ggplot(data = long_logistic_coverage %>%
               filter(method %in% c("Coverage1_const_signed", 
                                    "Coverage1_hc_signed",
                                    "Coverage1_const_unsigned", 
                                    "Coverage1_hc_unsigned"))) + 
  geom_line(aes(x = nsub, y = coverage, color = method, linetype = method)) + 
  facet_grid(
    error ~ S_label,
      labeller = labeller(S_label = label_parsed, error = label_value)
  ) + 
  theme_bw() + 
  geom_hline(yintercept = 0.95, linetype = "dotted") +
  labs(title = "Coverage", 
       x = "Number of subjects", y = "Coverage", color = "Method", 
       linetype = "Method") + 
  scale_x_continuous(breaks = c(100, 500, 1000, 1500), 
                     guide = guide_axis(angle = 45)) + 
  theme(legend.position = "top")  +
  scale_color_manual(values = coverage_color, labels = coverage_label) +
  scale_linetype_manual(values = coverage_linetype, labels = coverage_label)
```


```{r, fig.width=12, fig.height=5}
ggarrange(p1, p2, common.legend = T)
# ggsave("/media/disk2/asymptotic_resi/simulation/simresult_paper/logistic/bias_coverage.png", height = 5, width = 12, dpi = 600)
```

# Discarded

## Poisson

### const

```{r, eval=TRUE}
library(parallel) 
nsim = 1000
pi = 0.5
pi2 = 0.25
mc.cores = 20
ngroup = 2
py = 0.5

# generate effect sizes
# S(v)
es = c(seq(0, 0.4, length.out=5))
ns = c(seq(50, 200, by=50), 300, 400, 500, 600, 700, 800)
simResults = expand.grid(n=ns, S=es)

res_list <- list()
# Var(E(Y|X)) = Var(Y) - E (Var(Y|X))
# simulated diagnostic covariate
for(simInd in 1:nrow(simResults)){
  # get n and p for this simulation setting
  n = simResults[simInd, 'n']
  S = simResults[simInd, 'S']
  
  # The simulations assume that the sampling proportions are exactly pi (and 1-pi).
  # And also that they are not randomly selected across datasets.
  if(ngroup==2){
    dx <- rep(0:1, c(n * pi, n-n*pi))
    beta = S/(pi*(1-pi))
  } else {
    dx = factor(rep(0:2, c(n * pi, n*pi2, n *(1-pi-pi2))))
    beta = S/sqrt(sum(crossprod(scale(model.matrix(~ dx)[,-1], scale=F, center=TRUE)))/n)
  }
  cat('\r', c(S, n))
  
  
  res = do.call(rbind, mclapply(1:nsim, function(sim){
    # simulate the data
    dx = rbinom(n, 1, prob = pi) 
    beta = uniroot.all(solve_beta, interval = c(0, 10), S = S, px = 0.5, n = n)[1]
    lin_pred = rowSums(model.matrix(~ dx)[, -1, drop = FALSE] * beta) 
    Y = rbinom(n, 1, prob = locfit::expit(lin_pred))
    dat = data.frame(dx = dx, Y = Y)
    x = glm(Y ~ dx, data = dat, family = binomial)

    resires = resiParam(x, type = "const")
    resires
  }, mc.cores=mc.cores))
  
  
  res_list[[simInd]] = res
  
  simResults[simInd,"Mean RESI"] <- mean(res$resi)
  simResults[simInd,"Mean RESI2"] <- mean(res$resi2)
  simResults[simInd,"Var RESI"] <- var(res$resi)
  simResults[simInd,"Var Est"] <- mean(res$resiSE^2)
  simResults[simInd,"Var sqrt(n)A"] <- var(res$A) * n
  simResults[simInd,"Var sqrt(n)B"] <- var(res$B) * n
  simResults[simInd,"EstVar sqrt(n)A"] <- mean(res$Avar)
  simResults[simInd,"EstVar sqrt(n)B"] <- mean(res$Bvar)
  simResults[simInd,"Mean A"] <- mean(res$A)
  simResults[simInd,"Mean B"] <- mean(res$B)
  simResults[simInd,"Var sqrt(n)phi"] <- var(res$phi) * n
  simResults[simInd,"EstVar sqrt(n)phi"] <- mean(res$phivar)
  simResults[simInd,"Mean phi"] <- mean(res$phi)
  simResults[simInd,"Lcoverage"] <- mean(res$LCI<=S)
  simResults[simInd,"Ucoverage"] <- mean(res$UCI>=S)
  simResults[simInd,"coverage"] <- mean(res$LCI<=S & res$UCI>=S)
}

simResults_para <- simResults
```


# Examples
## LM

```{r}
# Simulate small data
set.seed(22)
pi = 0.5
pi2 = 0.25

# generate effect sizes
S = 0.5
n = 150
sigma = sqrt(2)

dx = rbinom(n, 1, prob = pi)
beta_true = sqrt(1/(pi*(1-pi)))*S * sigma
Y = rowSums(model.matrix(~ dx)[,-1, drop=FALSE]* beta_true) +
  matrix(rnorm(n, 0, sigma), nrow=n) # outcome
dat = data.frame(dx=dx, Y = Y)

fit_lm = lm(Y ~ dx, data=dat)
model = fit_lm
X = model.matrix(fit_lm)
type = "const"
variable = "dx"
source("/media/disk2/asymptotic_resi/functions.R")
# source("test/resiPEse_Th1_bounadry.R") # total derivative, theta = (phi, alpha, beta)
# source("test/resiPEse_Th2_norm.R") # partial derivative, theta = (phi, alpha, beta)
source("test/resiPEse_Th1.R") # total derivative, theta = (phi, alpha, beta)
# source("test/resiPEse_Th2.R") # partial derivative, theta = (phi, alpha, beta)
anova = TRUE

e <- resid(fit_lm)
sigma_hat <- summary(fit_lm)$sigma

sigma_S(S = S, X = X, idx = 2, pi = pi, 
        gamma1 = mean((e - mean(e))^3) / sigma_hat^3,
        kappa = mean((e - mean(e))^4) / sigma_hat^4,
        sigma = sigma)
resiPEse_Th1(fit_lm, variable = "dx")$RESI.SE


# resiPEse_Th1(fit_lm, variable = "dx", type = "const", anova = FALSE)
# resiPEse_Th1(fit_lm, variable = "dx", type = "HC3", anova = FALSE)
resi_pe(fit_lm, unbiased = FALSE)
resi_a_lm(model = fit_lm, variable = "dx", type = "HC3")
resiPEse_Th1(fit_lm, variable = "dx", type = "HC3", unsigned = FALSE)

# const
type = "const"
cat("const: \n")
## true
cat("true:", sigma^2 * solve(crossprod(X))[2,2]*n, "\n")
## function
cat("from Theorem 1:", resiPEse_Th1(fit_lm, variable = "dx", type = type, anova = anova)$Std.Error^2 * n, "\n")
cat("from Theorem 2:", resiPEse_Th2(fit_lm, variable = "dx", type = type, anova = anova)$Std.Error^2 * n, "\n")
## model
cat("from vcov:", vcov(fit_lm)[2,2] *n, "\n")
cat("\n")


# robust
type = "HC3"
cat("Robust: \n")
## true
cat("true:", sigma^2 * solve(crossprod(X))[2,2]*n, "\n")
## function
cat("from Theorem 1:", resiPEse_Th1(fit_lm, variable = "dx", type = type, anova = anova)$Std.Error^2 * n, "\n")
cat("from Theorem 2:", resiPEse_Th2(fit_lm, variable = "dx", type = type, anova = anova)$Std.Error^2 * n, "\n")
## model
cat("from vcovHC:", vcovHC(fit_lm, type)[2,2] *n, "\n")
```

## GLM

```{r, eval=FALSE}
set.seed(11)

# simulate the data
source("/media/disk2/asymptotic_resi/functions.R")
px <- 0.5
n = 150
a <- -2
S <- 0
dx = rbinom(n, 1, prob = px)
beta = uniroot.all(function(beta) S_squared(beta, a=a, px=px) - S^2,
                  lower = 0, upper = 10)[1]
lin_pred = rowSums(model.matrix(~ dx)[, -1, drop = FALSE] * beta + a) 
Y = rbinom(n, 1, prob = locfit::expit(lin_pred))
fit_glm <- glm(Y ~ dx, family = binomial)
model <- fit_glm
variable = "dx"
type = "HC3"
# source("test/resiPEse_Th1.R") # total derivative, theta = (phi, alpha, beta)
# source("test/resiPEse_Th2.R") # partial derivative, theta = (phi, alpha, beta)
anova = FALSE

# resiPEse_Th1(fit_glm, variable = "dx", type = "const", anova = FALSE)
# resiPEse_Th1(fit_glm, variable = "dx", type = "HC0", anova = FALSE)
resi_pe(fit_glm, unbiased = FALSE)

# const
type = "const"
cat("const: \n")
## true
cat("true:", var_sqrtn_beta_hat(alpha = a, beta = beta, px = px), "\n")
## function
cat("from Theorem 1:", resiPEse_Th1(fit_glm, type = type, variable = "dx")$Std.Error^2 * n, "\n")
cat("from Theorem 2:", resiPEse_Th2(fit_glm, type = type, variable = "dx")$Std.Error^2 * n, "\n")
## model
cat("from vcov:", vcov(fit_glm)[2,2] * n, "\n")


# const
type = "HC0"
cat("Robust: \n")
## true
cat("true:", var_sqrtn_beta_hat(alpha = a, beta = beta, px = px), "\n")
## function
cat("from Theorem 1:", resiPEse_Th1(fit_glm, type = type, variable = "dx")$Std.Error^2 * n, "\n")
cat("from Theorem 2:", resiPEse_Th2(fit_glm, type = type, variable = "dx")$Std.Error^2 * n, "\n")
## model
cat("from vcovHC:", vcovHC(fit_glm, type)[2,2] * n, "\n")
```

